Modeling the Linux page cache for accurate simulation of data-intensive applications

### 2020-12-18 paper_io_sim.tex
removed trailing comments

    The cache eviction simulation also runs in
    the main thread. It frees up the page cache by traversing and deleting
    least recently used clean data blocks in the inactive list.
    The amount of data to evict is passed as a parameter and data blocks are deleted
    from the inactive list until the evicted data reaches the required amount,
    or until there is no clean block left in the list.
    If the last evicted block does not have to be entirely evicted, the block is split in two blocks,
    and only one of them is evicted.
    The overhead of the cache eviction algorithm is not part of the simulated time
    since cache eviction time is negligible in real systems \tristan{a reference would be welcome}.

@@

        Simulated memory profiles were highly consistent with the real ones
        (Figure~\ref{fig:single_memprof}). With 20~GB files, memory profiles almost exactly matched the
        real ones, although dirty data seemed to be flushing faster in real
        life than in simulation, \tristan{any idea why?} a behavior also
        observed with 100~GB files. With 100~GB files, used memory reached
        total memory during the first write, triggering dirty data
        flushing, and droped back to cached memory when application tasks
        released anonymous memory. Simulated cached memory was highly
        consistent with real values, except toward the end of Read 3 where
        it slightly increased in simulation but not in reality. This
        occurred due to the fact that after Write 2, File 3 was only partially
        cached in simulation whereas it was entirely cached in the real
        system. In all cases, dirty data remained under the dirty ratio as
        expected. The Python prototype and \wrench-cache exhibited nearly
        identical memory profiles, which reinforces the confidence in our
        implementations.

>>>>

    The cache eviction simulation also runs in
    the main thread. It frees up the page cache by traversing and deleting
    least recently used clean data blocks in the inactive list.
    The amount of data to evict is passed as a parameter and data blocks are deleted
    from the inactive list until the evicted data reaches the required amount,
    or until there is no clean block left in the list.
    If the last evicted block does not have to be entirely evicted, the block is split in two blocks,
    and only one of them is evicted.
    The overhead of the cache eviction algorithm is not part of the simulated time
    since cache eviction time is negligible in real systems. % \tristan{a reference would be welcome}.

@@

        Simulated memory profiles were highly consistent with the real ones
        (Figure~\ref{fig:single_memprof}). With 20~GB files, memory profiles almost exactly matched the
        real ones, although dirty data seemed to be flushing faster in real
        life than in simulation, a behavior also
        observed with 100~GB files. With 100~GB files, used memory reached
        total memory during the first write, triggering dirty data
        flushing, and droped back to cached memory when application tasks
        released anonymous memory. Simulated cached memory was highly
        consistent with real values, except toward the end of Read 3 where
        it slightly increased in simulation but not in reality. This
        occurred due to the fact that after Write 2, File 3 was only partially
        cached in simulation whereas it was entirely cached in the real
        system. In all cases, dirty data remained under the dirty ratio as
        expected. The Python prototype and \wrench-cache exhibited nearly
        identical memory profiles, which reinforces the confidence in our
        implementations.
